Formalisation of Session-based Lambda Calculus Type Systems

### 2014-11-12 proposal/proposal.tex
Wrote up notes on Engineering Formal Metatheory paper.

POPLMARK
--------
SPL (+CPL)
* Most formalisations are informal, making it difficult to extend the development to a larger setting.
* Mistakes can easily slip into a development nullifying work
* Considerable manual effort must be expended to update all proofs to support an extension and it is not immediately obvious which definitions may need updated
* A lot of proof assistants offer a platform with which to study languages rigorously
WTD

>>>>

POPLMARK
--------
